{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Reconstitution of KL

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. 
	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$. Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

@@

	To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $X$ are defined as follows.

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator(cf. \cite{alexanderian_KLexpansion_2015}). Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.

	\begin{equation}
		{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
	\end{equation}

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.

	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
		\end{enumerate}
	\end{multicols}

>>>>

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}\hypertarget{KL}{}
	Given a realization of a random function realizing in $\mathbb{L}^2[0,1]$, it is possible to represent this realization in terms of its generating stochastic process. To obtain the analogous concept for a random function, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2[0,1]$. Therefore, let $X: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function. Then the mean and covariance functions of $X$ are defined as follows.
	%To motivate it, recall the representation of a random vector derived from the spectral decomposition of its covariance matrix. Let therefore $V(\omega)$ be a random vector realizing in $\mathbb{R}^{p}$ with $\mathbb{E}(V(\omega)) = \mu_V$ and $Cov(V(\omega)) = \Sigma_V$. Then $\Sigma_V$ can be expressed in terms of its Eigenvalues and orthonormal Eigenvectors as $\Sigma_V = \Gamma \Lambda \Gamma'$ using its Eigendecomposition.\\

@@

@@

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}\label{HSKernal}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda^{m}$ for all $m$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}). Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{N}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

	where the $\nu^m$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of ({\ref{HSKernal}}). The $\xi^{m}(\omega)$ satisfy following properties. %of the following equation.

	%\begin{equation}
	%	{\color{orange} [K \nu](t) =}\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
	%\end{equation}

	%The $\xi_j(\omega)$ are then given as 
	%\begin{equation}
	%	\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - %\mu(s)\right) \nu^m(s) \mathrm{d}s
	%\end{equation} 
	%and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector.
	\begin{multicols}{2}
		\begin{enumerate}
			\item $\mathbb{E}\left[\xi^m(\omega)\right] = 0$
			\item $Var\left(\xi^m(\omega)\right) = \lambda^m$
			\item $Cov\left(\xi^m(\omega), \xi^n(\omega)\right) = 0$ if $m \neq n$
		\end{enumerate}
	\end{multicols}
